### 2022-06-17 README.Rmd
update readme

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Ms.GSI

<!-- badges: start -->
<!-- badges: end -->

Ms.GSI is a package for conducting multistage genetic stock identification. This package includes functions to setup input data, run the multistage model, and make summary statistics and convergence diagnostics. It also includes a function for making trace plots.

## Installation

You can install the development version of Ms.GSI from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("boppingshoe/Ms.GSI")
```

## Example

This example shows a basic work flow for running a multistage model. First thing first, the background: we made up a scenario where we have samples for Chinook salmon by-catch from a Bering Sea fishery. The mixture sample contains fish from all over the north Pacific, but we are interested in the contribution from the Yukon River. We will conduct GSI using a broad-scale baseline (Templin) in combination with a regional baseline (Yukon) in a multistage framework.

The fake Chinook data sets are pre-loaded and included in the package. Here we prepare the input data:

```{r example prep data}

# library(Ms.GSI)
devtools::load_all()

msgsi_dat <-
  prep_msgsi_data(mixture_data = mix,
  baseline1_data = base_templin, baseline2_data = base_yukon,
  pop1_info = templin_pops211, pop2_info = yukon_pops50, sub_group = 3:5)

```

Using the prepared input data, we run the model with 150 iterations. In reality, you should of course run it with more iterations. We set the first 50 iterations as the warm-ups (not kept in the final output). Here's the summary for the estimates and convergence diagnostics.

```{r example run model}

msgsi_out <- msgsi_mdl(msgsi_dat, nreps = 150, nburn = 50, thin = 1, nchains = 4)

msgsi_out$summ_comb

```

There's a function to make trace plots and inspect mixing of chains.

```{r example trace plot}

tr_plot(obj = msgsi_out$trace_comb)

```

We also have a detailed document on the model and instructions (work in progress). Once you install the package, you can call the document using `vignette("Ms.GSI")`.

### 2022-06-17 R/data.R

@@ -24,6 +24,7 @@
 #' An example of genotype data for preparing msgsi input data
 #' in *rubias* format (but prep_msgsi_data() can also take GCL format)
 #' for making mixed population data
+#' This is a made up mixture sample, not real
 #'
 #' @format A tibble with 150 rows and 358 variables:
 #' @source ADF&G GCL database LOKI

### 2022-06-20 R/msgsi_data.R
tidy style

@@ -47,33 +47,41 @@ prep_msgsi_data <-
       dplyr::pull(locus)
 
     # check loci if provided
-    if(!is.null(loci1)) {
-      if(!all(loci_tier1 %in% loci1)) stop(c("Unidentified loci in baseline 1:", paste0(setdiff(loci_tier1, loci1), ", ")))
-    }
+    if (!is.null(loci1)) {
+      if (!all(loci_tier1 %in% loci1)) {
+        stop(c("Unidentified loci in baseline 1:", paste0(setdiff(loci_tier1, loci1), ", ")))
+      }
+      }
 
-    if(!is.null(loci2)) {
-      if(!all(loci_tier2 %in% loci2)) stop(c("Unidentified loci in baseline 2:", paste0(dplyr::setdiff(loci_tier2, loci2), ", ")))
-    }
+    if (!is.null(loci2)) {
+      if (!all(loci_tier2 %in% loci2)) {
+        stop(c("Unidentified loci in baseline 2:", paste0(dplyr::setdiff(loci_tier2, loci2), ", ")))
+      }
+      }
 
-    if(!is.null(loci1) & !is.null(loci2)) {
+    if (!is.null(loci1) & !is.null(loci2)) {
       loci_all =
         dplyr::tibble(locus = names(mixture_data)) %>%
         dplyr::filter(grepl("\\.1$", locus)) %>%
         dplyr::mutate(locus = substr(locus, 1, nchar(locus)-2)) %>%
         dplyr::pull(locus)
-      if(!all(c(loci_tier1, loci_tier2) %in% loci_all)) stop(c("Unidentified loci in mixture sample:", paste0(dplyr::setdiff(loci_all, c(loci_tier1, loci_tier2)), ", ")))
-    }
+      if (!all(c(loci_tier1, loci_tier2) %in% loci_all)) {
+        stop(c("Unidentified loci in mixture sample:", paste0(dplyr::setdiff(loci_all, c(loci_tier1, loci_tier2)), ", ")))
+      }
+      }
 
     # make sure group names are consistent between both tiers
-    if(any(!unique(pop2_info$repunit) %in% pop1_info$repunit)) stop(c("Group names are not consistent between the two baselines. Names in baseline 2 but not in baseline 1: ", unique(pop2_info$repunit)[!unique(pop2_info$repunit) %in% pop1_info$repunit]))
+    if (any(!unique(pop2_info$repunit) %in% pop1_info$repunit)) {
[…]

### 2022-06-20 R/msgsi_mdl.R

@@ -42,9 +42,7 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
   y <- dat_in$y %>% dplyr::select(dplyr::ends_with(as.character(0:9))) %>% dplyr::select(order(colnames(.))) %>% as.matrix() # base 1
   y2 <- dat_in$y2 %>% dplyr::select(dplyr::ends_with(as.character(0:9))) %>% dplyr::select(order(colnames(.))) %>% as.matrix() # base 2
 
-  if (is.null(dat_in$iden)) {
-    iden <- rep(NA, nrow(x))
-  } else iden <- dat_in$iden # age and iden info
+  if (is.null(dat_in$iden)) iden <- rep(NA, nrow(x)) else iden <- dat_in$iden # iden info
   nalleles <- dat_in$nalleles # number of allele types
   nalleles2 <- dat_in$nalleles2 # number of allele types
   grps <- dat_in$groups # vector id for the 1st tier reporting groups (aka groupvec)
@@ -72,13 +70,12 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
 
   ### specifications ### ----
   rdirich <- function(alpha0) {
-    if (sum(alpha0)) {
+    if (sum(alpha0) > 0) {
       vec = stats::rgamma(length(alpha0), alpha0, 1)
       vec = vec / sum(vec)
       vec[vec == 0] = .Machine$double.xmin
       vec
-    }
-    else{
+    } else {
       rep(0, length(alpha0))
     }
   } # og random dirichlet by jj
@@ -86,7 +83,7 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
   message(paste0("Running model (and the category is... ", sample(categories, 1), "!)"))
   run_time <- Sys.time()
 
-  if (cond_gsi) nadapt = 0
+  if (isTRUE(cond_gsi)) nadapt = 0
   n_burn <- ifelse(keep_burn, 0, nburn)
 
   chains <- seq(nchains)
@@ -97,11 +94,8 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
   ### initial values ### ----
   ## tier 1
   # hyper-param for relative freq q (allele)
-  beta <-
-    matrix(0,
[…]

### 2022-06-20 R/trace_plot.R

@@ -29,7 +29,7 @@ tr_plot <- function (obj, nburn = 0, thin = 1, name_order = NULL) {
     name_order <- dplyr::select(obj, -c(itr, chain)) %>% colnames()
   }
 
-  tidyr::pivot_longer({{obj}}, cols = -c(chain, itr)) %>%
+  tidyr::pivot_longer({{ obj }}, cols = -c(chain, itr)) %>%
     dplyr::mutate(name = factor(name, levels = name_order)) %>%
     ggplot2::ggplot() +
     ggplot2::geom_line(ggplot2::aes(x = itr, y = value, color = factor(chain))) +

### 2022-06-20 R/msgsi_data.R
more tidy styling

@@ -1,13 +1,20 @@
 
 #' Preparing multistage GSI input data
 #'
-#' @param mixture_data Individual fish with loci for both tier 1 and tier 2. Mixture data in GCL or *rubias* format.
+#' @param mixture_data Individual fish with loci for both tier 1 and tier 2.
+#'   Mixture data in GCL or *rubias* format.
 #' @param baseline1_data Tier 1 baseline data in GCL or *rubias* format.
 #' @param baseline2_data Tier 2 baseline data in GCL or *rubias* format.
-#' @param pop1_info Population information for tier 1. A tibble with columns collection (collection names), repunit (reporting unit names), grpvec (group numbers), origin (wild/hatchery).
-#' @param pop2_info Population information for tier 2. A tibble with columns collection (collection names), repunit (reporting unit names), grpvec (group numbers).
-#' @param sub_group Group numbers for groups of interest. Group id numbers in tier 1 that identify groups in tier 2.
-#' @param file_path Where you want to save a copy of input data. Leave it empty if you don't want to save a copy.
+#' @param pop1_info Population information for tier 1. A tibble with columns
+#'   collection (collection names), repunit (reporting unit names),
+#'   grpvec (group numbers), origin (wild/hatchery).
+#' @param pop2_info Population information for tier 2. A tibble with columns
+#'   collection (collection names), repunit (reporting unit names),
+#'   grpvec (group numbers).
+#' @param sub_group Group numbers for groups of interest. Group id numbers in tier
+#'   1 that identify groups in tier 2.
+#' @param file_path Where you want to save a copy of input data. Leave it empty if
+#'   you don't want to save a copy.
 #' @param loci1 Optional. Provide loci (for tier 1) as a fail-safe check.
 #' @param loci2 Optional. Provide loci (for tier 2) as a fail-safe check.
 #'
@@ -21,8 +28,6 @@
 #'   prep_msgsi_data(mixture_data = mix,
 #'   baseline1_data = base_templin, baseline2_data = base_yukon,
 #'   pop1_info = templin_pops211, pop2_info = yukon_pops50, sub_group = 3:5)
-
-
 prep_msgsi_data <-
   function(mixture_data, baseline1_data, baseline2_data,
            pop1_info, pop2_info, sub_group,
[…]

### 2022-06-20 R/msgsi_mdl.R

@@ -6,13 +6,18 @@
 #' @param nburn Number of warm-up runs.
 #' @param thin Frequency to thin the output.
 #' @param nchains Number of independent MCMC processes.
-#' @param nadapt Number of adaptation run (default is 0). Only available when running model in fully Bayesian mode.
+#' @param nadapt Number of adaptation run (default is 0). Only available when
+#'   running model in fully Bayesian mode.
 #' @param keep_burn To save the burn-ins or not (default is FALSE).
 #' @param cond_gsi To run the model in conditional GSI mode (default is TRUE).
-#' @param out_path File path to save the output. Leave it empty is you don't want to save the output.
+#' @param out_path File path to save the output. Leave it empty is you don't
+#'   want to save the output.
 #' @param seed Random seed for reproducibility. Default is NULL (no random seed).
 #'
-#' @return A list contains reporting group proportion summary and trace for tier 1 (summ_t1, trace_t1), tier 2 (summ_t2, trace_t2) and two tiers combined (summ_comb, trace_comb), and record of individual assignment during first tier for each individual (idens).
+#' @return A list contains reporting group proportion summary and trace for
+#'   tier 1 (summ_t1, trace_t1), tier 2 (summ_t2, trace_t2) and two tiers
+#'   combined (summ_comb, trace_comb), and record of individual assignment
+#'   during first tier for each individual (idens).
 #'
 #' @export
 #' @importFrom magrittr %>%
@@ -28,7 +33,6 @@
 #'
 #' # run multistage model
 #' msgsi_out <- msgsi_mdl(msgsi_dat, nreps = 25, nburn = 15, thin = 1, nchains = 1)
-
 msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn = FALSE, cond_gsi = TRUE, out_path = NULL, seed = NULL) {
 
   ### load required packages ### ----
@@ -37,10 +41,22 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
[…]

### 2022-06-20 R/trace_plot.R

@@ -2,9 +2,12 @@
 #' Plot MCMC trace
 #'
 #' @param obj Trace from the model output.
-#' @param nburn Number of burn-in you set up when you ran the model. Default is 0 if you didn't save the burn-ins (keep_burn = FALSE).
-#' @param thin Number of thinning you set up when you ran the model. Default is 1 (no thinning).
-#' @param name_order Arrange the reporting groups as you wish. Leave it empty if you want to accept the default.
+#' @param nburn Number of burn-in you set up when you ran the model.
+#'   Default is 0 if you didn't save the burn-ins (keep_burn = FALSE).
+#' @param thin Number of thinning you set up when you ran the model.
+#'   Default is 1 (no thinning).
+#' @param name_order Arrange the reporting groups as you wish. Leave it empty
+#'   if you want to accept the default.
 #'
 #' @return Trace plot in ggplot
 

### 2022-06-20 R/msgsi_data.R
yet more tidy styling

@@ -34,51 +34,39 @@ prep_msgsi_data <-
            file_path = NULL,
            loci1 = NULL, loci2 = NULL) {
 
-    start_time = Sys.time()
-    message("Working on it, may take a minute or two...")
+    start_time <- Sys.time()
 
     # identify loci for each stage
     # make sure no colnames other than marker names have ".1" at the end
-    loci_tier1 =
+    loci_tier1 <-
       dplyr::tibble(locus = names(baseline1_data)) %>%
       dplyr::filter(grepl("\\.1$", locus)) %>%
       dplyr::mutate(locus = substr(locus, 1, nchar(locus)-2)) %>%
       dplyr::pull(locus)
 
-    loci_tier2 =
+    loci_tier2 <-
       dplyr::tibble(locus = names(baseline2_data)) %>%
       dplyr::filter(grepl("\\.1$", locus)) %>%
       dplyr::mutate(locus = substr(locus, 1, nchar(locus)-2)) %>%
       dplyr::pull(locus)
 
-    # check loci if provided
-    if (!is.null(loci1)) {
-      if (!all(loci_tier1 %in% loci1)) {
-        stop(c("Unidentified loci in baseline 1:", paste0(setdiff(loci_tier1, loci1), ", ")))
-      }
-      }
+    # input error check
 
-    if (!is.null(loci2)) {
-      if (!all(loci_tier2 %in% loci2)) {
-        stop(c("Unidentified loci in baseline 2:", paste0(dplyr::setdiff(loci_tier2, loci2), ", ")))
-      }
-      }
+    loci_all <-
+      dplyr::tibble(locus = names(mixture_data)) %>%
+      dplyr::filter(grepl("\\.1$", locus)) %>%
+      dplyr::mutate(locus = substr(locus, 1, nchar(locus) - 2)) %>%
+      dplyr::pull(locus)
 
-    if (!is.null(loci1) & !is.null(loci2)) {
-      loci_all =
-        dplyr::tibble(locus = names(mixture_data)) %>%
-        dplyr::filter(grepl("\\.1$", locus)) %>%
-        dplyr::mutate(locus = substr(locus, 1, nchar(locus)-2)) %>%
-        dplyr::pull(locus)
-      if (!all(c(loci_tier1, loci_tier2) %in% loci_all)) {
[…]

### 2022-06-20 R/msgsi_mdl.R

@@ -35,9 +35,6 @@
 #' msgsi_out <- msgsi_mdl(msgsi_dat, nreps = 25, nburn = 15, thin = 1, nchains = 1)
 msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn = FALSE, cond_gsi = TRUE, out_path = NULL, seed = NULL) {
 
-  ### load required packages ### ----
-  # pacman::p_load(doParallel, parallel, foreach, tidyverse, doRNG, coda)
-
   categories <- c("Live, Werk, Pose", "Bring It Like Royalty", "Face", "Best Mother", "Best Dressed", "High Class In A Fur Coat", "Snow Ball", "Butch Queen Body", "Weather Girl", "Labels", "Mother-Daughter Realness", "Working Girl", "Linen Vs. Silk", "Perfect Tens", "Modele Effet", "Stone Cold Face", "Realness", "Intergalatic Best Dressed", "House Vs. House", "Femme Queen Vogue", "High Fashion In Feathers", "Femme Queen Runway", "Lofting", "Higher Than Heaven", "Once Upon A Time")
 
   ### data input ### ----
@@ -192,7 +189,9 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
   p2 <- rdirich(table(iden2) + pPrior2)
 
   ### parallel chains ### ----
-  out_list0 <- foreach::foreach(ch = chains, .packages = c("magrittr", "tidyr", "dplyr")) %dorng% {
+  out_list0 <- foreach::foreach(
+    ch = chains, .packages = c("magrittr", "tidyr", "dplyr")
+    ) %dorng% {
 
     p_out <- p2_out <- pp2_out <- iden_out <- list()
 
@@ -272,13 +271,11 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
 
     } # end gibbs loop
 
-    out_ch <- lapply(list(p_out, p2_out, pp2_out, iden_out), function(out) {
+    lapply(list(p_out, p2_out, pp2_out, iden_out), function(out) {
       sapply(out, rbind) %>%
         t() %>%
         dplyr::as_tibble()
     })
-
-    out_ch
 
   } # end parallel chains
 
[…]

### 2022-06-30 README.Rmd
yet more tidy styling
updates

@@
 
-Ms.GSI is a package for conducting multistage genetic stock identification.
+Ms.GSI is here to help you conducting multistage genetic stock identification.
 This package includes functions to setup input data, run the multistage model, and make summary statistics and convergence diagnostics.
@@
 This example shows a basic work flow for running a multistage model.
-First thing first, the background: we made up a scenario where we have samples for Chinook salmon by-catch from a Bering Sea fishery.
-The mixture sample contains fish from all over the north Pacific, but we are interested in the contribution from the Yukon River.
-We will conduct GSI using a broad-scale baseline (Templin) in combination with a regional baseline (Yukon) in a multistage framework.
+First thing first, the background: we made up a scenario where we have samples for Chinook salmon bycatch from Bering Sea groundfish fisheries.
+The mixture sample contains Chinook from all over North Pacific, but we are interested in contribution from the Yukon River.
+We will conduct GSI using a broad-scale baseline (`base_templin`) in combination with a regional baseline (`base_yukon`) in a multistage framework.
 
@@
 
-```{r example prep data}
+```{r example_prep_data}
 
@@
 
-Using the prepared input data, we run the model with 150 iterations.
+Using the prepared input data, we run the model with four chains of 150 iterations.
 In reality, you should of course run it with more iterations.
-We set the first 50 iterations as the warm-ups (not kept in the final output).
+We set the first 50 iterations in each chain as the warm-ups (not kept in the final output).
 Here's the summary for the estimates and convergence diagnostics.
 
-```{r example run model}
+```{r example_run_model}
 
@@
 
-There's a function to make trace plots and inspect mixing of chains.
+There's a function in the package to make trace plots and inspect mixing of chains.
 
-```{r example trace plot}
+```{r example_trace_plot}
 

### 2022-06-30 R/msgsi_data.R

@@ -41,13 +41,13 @@ prep_msgsi_data <-
     loci_tier1 <-
       dplyr::tibble(locus = names(baseline1_data)) %>%
       dplyr::filter(grepl("\\.1$", locus)) %>%
-      dplyr::mutate(locus = substr(locus, 1, nchar(locus)-2)) %>%
+      dplyr::mutate(locus = substr(locus, 1, nchar(locus) - 2)) %>%
       dplyr::pull(locus)
 
     loci_tier2 <-
       dplyr::tibble(locus = names(baseline2_data)) %>%
       dplyr::filter(grepl("\\.1$", locus)) %>%
-      dplyr::mutate(locus = substr(locus, 1, nchar(locus)-2)) %>%
+      dplyr::mutate(locus = substr(locus, 1, nchar(locus) - 2)) %>%
       dplyr::pull(locus)
 
     # input error check
@@ -241,23 +241,23 @@ check_loci_pops <- function(loci1_pr, loci_t1, loci2_pr, loci_t2,
 
   # check loci if provided
   if (!is.null(loci1_pr)) {
-    if (!all(loci_t1 %in% loci1_pr)) {
-      return(c("Unidentified loci in baseline 1: ",
-               paste0(setdiff(loci_t1, loci1_pr), ", ")))
+    if (!setequal(loci_t1, loci1_pr)) {
+      return(c("Unidentified loci in baseline 1 or provided list: ",
+               paste0(c(setdiff(loci_t1, loci1_pr), setdiff(loci1_pr, loci_t1)), ", ")))
     }
   }
 
   if (!is.null(loci2_pr)) {
-    if (!all(loci_t2 %in% loci2_pr)) {
-      return(c("Unidentified loci in baseline 2: ",
-               paste0(dplyr::setdiff(loci_t2, loci2_pr), ", ")))
+    if (!setequal(loci_t2, loci2_pr)) {
+      return(c("Unidentified loci in baseline 2 or provided list: ",
+               paste0(c(setdiff(loci_t2, loci2_pr) | setdiff(loci2_pr, loci_t2)), ", ")))
     }
   }
 
   if (!is.null(loci1_pr) & !is.null(loci2_pr)) {
-    if (!all(c(loci_t1, loci_t2) %in% loc_all)) {
-      return(c("Unidentified loci in mixture sample: ",
-               paste0(dplyr::setdiff(loc_all, c(loci_t1, loci_t2)), ", ")))
[…]

### 2022-06-30 R/msgsi_mdl.R

@@ -385,7 +385,7 @@ summ_func <- function(combo_file, keeplist, mc_file, groupnames, n_ch) {
     tidyr::pivot_longer(cols = tidyr::everything()) %>%
     dplyr::group_by(name) %>%
     dplyr::summarise(
-      mean = base::mean(value),
+      mean = mean(value),
       median = stats::median(value),
       sd = stats::sd(value),
       ci.05 = stats::quantile(value, 0.05),

### 2022-07-01 data-raw/bering_yukon.R
fix typo in pop info table

@@ -13,9 +13,11 @@ yukon_loci177 <- yukon_loci380panel %>% filter(Panel == "Chinook_IDFG_299") %>% 
 
 CreateLocusControl.GCL(locusnames=yukon_loci177, username="bhsu", password=password)
 
-templin_pops211 <- read_csv(paste0(wd, "/projects/imbalanced_baseline/ayk_bering_juv_king/Baseline_Templin/baseline_Templin_pops_211_info.csv"))
+templin_pops211 <- read_csv(paste0(wd, "/projects/imbalanced_baseline/ayk_bering_juv_king/Baseline_Templin/baseline_Templin_pops_211_info.csv")) %>%
+  mutate(popSILLY = case_when(popSILLY == "KCHUN09.KCHUN12plate1" ~ "KCHUN09.KCHUN12",
+                              TRUE ~ popSILLY))
 templin_sillys211 <- templin_pops211 %>% pull(popSILLY)
-templin_sillys211[87] <- "KCHUN09.KCHUN12" # I think there's a typo
+# templin_sillys211[87] <- "KCHUN09.KCHUN12" # I think there's a typo
 templin_sillys_all <- str_split(templin_sillys211, pattern = "[.]") %>% unlist
 
 yukon_pops50 <- read_csv(paste0(wd, "/projects/imbalanced_baseline/ayk_bering_juv_king/baseline_yukon/50pop_groupvecs.csv"))

### 2022-07-01 R/msgsi_data.R
edit known_colection to recognize collection names

@@ -70,28 +70,28 @@ prep_msgsi_data <-
 
     # change column name if the data are gcl objects
     # to match rubias input data name convention
-    if ("SILLY_CODE" %in% names(baseline1_data)) baseline1_data = dplyr::rename(baseline1_data, collection = SILLY_CODE)
+    if ("SILLY_CODE" %in% names(baseline1_data)) baseline1_data <- dplyr::rename(baseline1_data, collection = SILLY_CODE)
 
-    if ("SILLY_CODE" %in% names(baseline2_data)) baseline2_data = dplyr::rename(baseline2_data, collection = SILLY_CODE)
+    if ("SILLY_CODE" %in% names(baseline2_data)) baseline2_data <- dplyr::rename(baseline2_data, collection = SILLY_CODE)
 
-    if ("SillySource" %in% names(mixture_data)) mixture_data = dplyr::rename(mixture_data, indiv = SillySource)
+    if ("SillySource" %in% names(mixture_data)) mixture_data <- dplyr::rename(mixture_data, indiv = SillySource)
 
     # tally allele for each baseline and mixture sample
-    base1 = allefreq(baseline1_data, baseline1_data, loci_tier1, collect_by = collection) %>%
+    base1 <- allefreq(baseline1_data, baseline1_data, loci_tier1, collect_by = collection) %>%
       dplyr::right_join(pop1_info, by = c("collection" = "collection"), keep = FALSE) %>%
       dplyr::relocate(!dplyr::ends_with(as.character(0:9)), .after = collection) %>%
       dplyr::mutate(dplyr::across(dplyr::ends_with(as.character(0:9)), ~tidyr::replace_na(., 0)))
 
-    base2 = allefreq(baseline2_data, baseline2_data, loci_tier2, collect_by = collection) %>%
+    base2 <- allefreq(baseline2_data, baseline2_data, loci_tier2, collect_by = collection) %>%
       dplyr::right_join(pop2_info, by = c("collection" = "collection"), keep = FALSE) %>%
       dplyr::relocate(!dplyr::ends_with(as.character(0:9)), .after = collection)
 
-    mix1 = allefreq(mixture_data, baseline1_data, loci_tier1)
+    mix1 <- allefreq(mixture_data, baseline1_data, loci_tier1)
 
-    mix2 = allefreq(mixture_data, baseline2_data, loci_tier2)
[…]

### 2022-07-01 tests/testthat.R
initiate tests

@@ -1,0 +1,12 @@
+# This file is part of the standard setup for testthat.
+# It is recommended that you do not modify it.
+#
+# Where should you do additional test configuration?
+# Learn more about the roles of various files in:
+# * https://r-pkgs.org/tests.html
+# * https://testthat.r-lib.org/reference/test_package.html#special-files
+
+library(testthat)
+library(Ms.GSI)
+
+test_check("Ms.GSI")

### 2022-07-01 tests/testthat/test-msgsi_data.R

@@ -1,0 +1,32 @@
+
+# devtools::load_all()
+
+test_that("data error check", {
+
+  loci_t1 <- dplyr::tibble(locus = names(base_templin)) %>%
+    dplyr::filter(grepl("\\.1$", locus)) %>%
+    dplyr::mutate(locus = substr(locus, 1, nchar(locus) - 2)) %>%
+    dplyr::pull(locus)
+
+  loci_t2 <- dplyr::tibble(locus = names(base_yukon)) %>%
+    dplyr::filter(grepl("\\.1$", locus)) %>%
+    dplyr::mutate(locus = substr(locus, 1, nchar(locus) - 2)) %>%
+    dplyr::pull(locus)
+
+  expect_error(prep_msgsi_data(mix, base_templin, base_yukon,
+                               templin_pops211, yukon_pops50, 3:5,
+                               loci1 = loci_t1[-1]),
+               "Unidentified loci in baseline 1")
+
+  expect_error(prep_msgsi_data(mix, base_templin, base_yukon,
+                               templin_pops211, yukon_pops50, 3:5,
+                               loci2 = c(loci_t2, "plus_one")),
+               "Unidentified loci in baseline 2")
+
+  expect_error(prep_msgsi_data(mix, base_templin,
+                               dplyr::mutate(base_yukon, plus_one = 0, plus_one.1 = 0),
+                               templin_pops211, yukon_pops50, 3:5,
+                               loci1 = loci_t1, loci2 = c(loci_t2, "plus_one")),
+               "Unidentified loci in mixture")
+
+})

### 2022-07-01 R/msgsi_data.R
found error with test!

@@ -272,7 +272,7 @@ check_loci_pops <- function(loci1_pr, loci_t1, loci2_pr, loci_t2,
   if (!is.null(loci2_pr)) {
     if (!setequal(loci_t2, loci2_pr)) {
       return(c("Unidentified loci in baseline 2 or provided list: ",
-               paste0(c(setdiff(loci_t2, loci2_pr) | setdiff(loci2_pr, loci_t2)), ", ")))
+               paste0(c(setdiff(loci_t2, loci2_pr), setdiff(loci2_pr, loci_t2)), ", ")))
     }
   }
 

### 2022-07-05 tests/testthat/test-msgsi_data.R
test for error check

@@ -29,4 +29,31 @@ test_that("data error check", {
                                loci1 = loci_t1, loci2 = c(loci_t2, "plus_one")),
                "Unidentified loci in mixture")
 
+  expect_error(prep_msgsi_data(mix, base_templin, base_yukon,
+                               templin_pops211,
+                               dplyr::mutate(yukon_pops50,
+                                             repunit = dplyr::case_when(
+                                               repunit == "Lower Yukon" ~ "wrong yukon",
+                                               TRUE ~ repunit
+                                             )),
+                               sub_group = 3:5),
+               "Group names are not consistent")
+
+  expect_error(prep_msgsi_data(dplyr::mutate(mix,
+                                             known_coll = c("KANDR02", rep(NA, 149))),
+                               base_templin, base_yukon,
+                               templin_pops211, yukon_pops50, 3:5),
+               "Unidentified populations found in 'known_collection'")
+
 })
+
+
+
+
+
+
+
+
+
+
+

### 2022-07-05 R/msgsi_data.R
stats package

@@ -148,9 +148,9 @@ prep_msgsi_data <-
       iden <- mixture_data %>%
         dplyr::select(tidyr::contains("known_")) %>%
         dplyr::pull()
-      if (!all(na.omit(iden) %in% c(wildpops, hatcheries))) {
+      if (!all(stats::na.omit(iden) %in% c(wildpops, hatcheries))) {
         stop(c("Unidentified populations found in 'known_collection': ",
-               paste0(unique(na.omit(iden)[which(!na.omit(iden) %in% c(wildpops, hatcheries))]), ", ")))
+               paste0(unique(stats::na.omit(iden)[which(!stats::na.omit(iden) %in% c(wildpops, hatcheries))]), ", ")))
       }
       iden <- factor(iden, levels = c(wildpops, hatcheries)) %>%
         as.numeric()

### 2022-07-05 tests/testthat/test-msgsi_data.R
clean up test file

@@ -1,6 +1,4 @@
 
-# devtools::load_all()
-
 test_that("data error check", {
 
   loci_t1 <- dplyr::tibble(locus = names(base_templin)) %>%

### 2022-07-06 README.Rmd
update README to include info on vignette

@@
 
-Ms.GSI is here to help you conducting multistage genetic stock identification.
+*Ms.GSI* is here to help you conducting multistage genetic stock identification.
 This package includes functions to setup input data, run the multistage model, and make summary statistics and convergence diagnostics.
@@
 
-You can install the development version of Ms.GSI from [GitHub](https://github.com/) with:
+You can install the development version of *Ms.GSI* from [GitHub](https://github.com/boppingshoe/Ms.GSI) with:
 
@@
 # install.packages("devtools")
-devtools::install_github("boppingshoe/Ms.GSI")
+devtools::install_github("boppingshoe/Ms.GSI", build_vignettes = TRUE)
 ```
@@
 
-This example shows a basic work flow for running a multistage model.
+This example shows the basic workflows for running a multistage model.
 First thing first, the background: we made up a scenario where we have samples for Chinook salmon bycatch from Bering Sea groundfish fisheries.
-The mixture sample contains Chinook from all over North Pacific, but we are interested in contribution from the Yukon River.
+The mixture sample contains Chinook from all over the North Pacific, but we are interested in contribution from the Yukon River.
 We will conduct GSI using a broad-scale baseline (`base_templin`) in combination with a regional baseline (`base_yukon`) in a multistage framework.
 
-The fake Chinook data sets are pre-loaded and included in the package. Here we prepare the input data:
+The fake Chinook data sets are pre-loaded in the *Ms.GSI* package. Here we prepare the input data:
 
@@
 
-# library(Ms.GSI)
-devtools::load_all()
+library(Ms.GSI)
 
@@
 
-We also have a detailed document on the model and instructions (work in progress). Once you install the package, you can call the document using `vignette("Ms.GSI")`.
+We also documented in details on the mathematical model of multistage framework and instructions for using *Ms.GSI* package.
+Once you installed *Ms.GSI*, you can call the document using `vignette("msgsi_vignette")`.

### 2022-07-08 R/msgsi_data.R
allow group names to be different between baselines, but give warning

@@ -62,7 +62,10 @@ prep_msgsi_data <-
                                      pop1_info$repunit, pop2_info$repunit,
                                      loci_all)
 
-    if ("all good" %in% error_message) {
+    if (grepl("Group names", error_message[1])) {
+      warning(error_message)
+      message("Compiling input data, may take a minute or two...")
+    } else if ("all good" %in% error_message) {
       message("Compiling input data, may take a minute or two...")
     } else {
       stop(error_message)

### 2022-07-08 tests/testthat/test-msgsi_data.R

@@ -27,7 +27,7 @@ test_that("data error check", {
                                loci1 = loci_t1, loci2 = c(loci_t2, "plus_one")),
                "Unidentified loci in mixture")
 
-  expect_error(prep_msgsi_data(mix, base_templin, base_yukon,
+  expect_warning(prep_msgsi_data(mix, base_templin, base_yukon,
                                templin_pops211,
                                dplyr::mutate(yukon_pops50,
                                              repunit = dplyr::case_when(

### 2022-08-15 R/msgsi_data.R
use unlist() to pull both score columns

@@ -98,7 +98,7 @@ prep_msgsi_data <-
       dplyr::tibble(locus = loc,
                     call = baseline1_data %>%
                       dplyr::select(dplyr::all_of(loc), paste0(loc, ".1")) %>%
-                      dplyr::pull() %>% unique() %>% .[!is.na(.)],
+                      unlist() %>% unique() %>% .[!is.na(.)],
                     altyp = seq.int(dplyr::n_distinct(call)) %>% factor())
     }) %>% dplyr::bind_rows() %>%
       dplyr::group_by(locus) %>%
@@ -112,7 +112,7 @@ prep_msgsi_data <-
       dplyr::tibble(locus = loc,
                     call = baseline2_data %>%
                       dplyr::select(dplyr::all_of(loc), paste0(loc, ".1")) %>%
-                      dplyr::pull() %>% unique() %>% .[!is.na(.)],
+                      unlist() %>% unique() %>% .[!is.na(.)],
                     altyp = seq.int(dplyr::n_distinct(call)) %>% factor())
     }) %>% dplyr::bind_rows() %>%
       dplyr::group_by(locus) %>%
@@ -205,7 +205,7 @@ allefreq <- function(gble_in, gble_ref, loci, collect_by = indiv) {
     dplyr::tibble(locus = loc,
                   call = gble_ref %>%
                     dplyr::select(dplyr::all_of(loc), paste0(loc, ".1")) %>%
-                    dplyr::pull() %>%
+                    unlist() %>%
                     unique() %>%
                     .[!is.na(.)],
                   altyp = seq.int(dplyr::n_distinct(call)) %>% factor)

### 2023-02-10 R/indiv_assign.R
individual assignment summary

@@ -1,0 +1,43 @@
+
+#' Individual assignment summary
+#'
+#' @param mdl_out Model output object name.
+#' @param mdl_dat Input data object name.
+#'
+#' @return Individual assignment summary
+#' @importFrom magrittr %>%
+#' @export
+#'
+#' @examples
+#' # set up input data and run multistage model
+#' msgsi_dat <-
+#'   prep_msgsi_data(mixture_data = mix,
+#'   baseline1_data = base_templin, baseline2_data = base_yukon,
+#'   pop1_info = templin_pops211, pop2_info = yukon_pops50, sub_group = 3:5)
+#'
+#' msgsi_out <- msgsi_mdl(msgsi_dat, nreps = 25, nburn = 15, thin = 1, nchains = 1)
+#'
+#' # trace plot
+#' ind_iden <- indiv_assign(msgsi_out, msgsi_dat)
+#'
+indiv_assign <- function(mdl_out, mdl_dat) {
+  regional <- which(mdl_dat$groups %in% mdl_dat$sub_group)
+
+  pho <- apply(mdl_out$idens_t1, 2,
+               function (idens) mean(idens %in% regional))
+
+  pi <- apply(mdl_out$idens_t2, 2,
+              function (idens) {
+                factor(idens, levels = seq(length(mdl_dat$p2_groups))) %>%
+                  table(.) %>%
+                  tapply(., mdl_dat$p2_groups, sum) %>%
+                  prop.table(.)
+              })
+
+  tidyr::tibble(ID = mdl_dat$x$indiv) %>%
+    dplyr::bind_cols({
+      cbind(1 - pho, pho * t(pi)) %>%
+        tidyr::as_tibble() %>%
+        stats::setNames(c("Not regional", mdl_dat$group_names_t2))
+    })
+}

### 2023-02-13 R/indiv_assign.R
As_tibble needs column names

@@ -37,7 +37,7 @@ indiv_assign <- function(mdl_out, mdl_dat) {
   tidyr::tibble(ID = mdl_dat$x$indiv) %>%
     dplyr::bind_cols({
       cbind(1 - pho, pho * t(pi)) %>%
-        tidyr::as_tibble() %>%
+        as.data.frame() %>%
         stats::setNames(c("Not regional", mdl_dat$group_names_t2))
     })
 }

### 2023-02-13 README.Rmd
web site initiate

@@
 
-We also documented in details on the mathematical model of multistage framework and instructions for using *Ms.GSI* package.
-Once you installed *Ms.GSI*, you can call the document using `vignette("msgsi_vignette")`.
+Details of the mathematical model of integrated multistage framework and instructions for using *Ms.GSI* package can be found in the "articles" tab of the package website.
+Or, once you installed *Ms.GSI*, you can call the article using `vignette("msgsi_vignette")`.

### 2023-09-14 R/msgsi_mdl.R
move freq2 because not updated for cond GSI

@@ -153,7 +153,7 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
     (1 / table(grps) / max(grps))[grps]
 
   iden[na_i] <- unlist(lapply(na_i, function(m) {
-    sample(K, 1, FALSE, (pPrior * freq[m, ])[seq.int(K)])
+    sample(K, 1, FALSE, (pPrior * freq[m, ])[seq.int(K)]) # only for wild pops
   }))
 
   p <- rdirich(table(iden) + pPrior)
@@ -229,6 +229,8 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
           unlist(tapply(rw, INDEX = trait_fac2, FUN = rdirich))
         })
 
+        freq2 <- exp(x2 %*% log(t_q2))
+
       } # if no cond_gsi
 
       iden[na_i] <- unlist( lapply(na_i, function(m) {
@@ -245,8 +247,6 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
       } # do this to help prevent no iden == sub_grp (when 1st tier markers are shit)
 
       p <- rdirich(table(iden) + pPrior)
-
-      freq2 <- exp(x2 %*% log(t_q2))
 
       iden2 <- apply(freq2, 1, function(frq_rw) {
         sample(nrow(y2), 1, FALSE, (p2 * frq_rw))

### 2025-04-19 R/indiv_assign.R
trace as collections

@@ -24,18 +24,18 @@
 indiv_assign <- function(mdl_out, mdl_dat) {
   p <- apply(mdl_out$idens_t1, 2,
              function (idens) {
-               factor(idens, levels = seq(length(mdl_dat$groups))) %>%
+               factor(idens, levels = seq(length(mdl_dat$groups$grpvec))) %>%
                  table(.) %>%
                  prop.table(.)
-             }) %>% rowsum(., mdl_dat$groups) %>% t()
+             }) %>% rowsum(., mdl_dat$groups$grpvec) %>% t()
   pho <- rowSums(p[, mdl_dat$sub_group])
 
   pi <- apply(mdl_out$idens_t2, 2,
               function (idens) {
-                factor(idens, levels = seq(length(mdl_dat$p2_groups))) %>%
+                factor(idens, levels = seq(length(mdl_dat$p2_groups$grpvec))) %>%
                   table(.) %>%
                   prop.table(.)
-              }) %>% rowsum(., mdl_dat$p2_groups) %>% t()
+              }) %>% rowsum(., mdl_dat$p2_groups$grpvec) %>% t()
 
     tidyr::tibble(ID = mdl_dat$x$indiv) %>%
     dplyr::bind_cols({

### 2025-04-19 R/msgsi_mdl.R

@@ -69,8 +69,8 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
   if (is.null(dat_in$iden)) iden <- rep(NA, nrow(x)) else iden <- dat_in$iden # iden info
   nalleles <- dat_in$nalleles # number of allele types
   nalleles2 <- dat_in$nalleles2 # number of allele types
-  grps <- dat_in$groups # vector id for the 1st tier reporting groups (aka groupvec)
-  p2_grps <- dat_in$p2_groups # vector id for the 2nd tier reporting groups
+  grps <- dat_in$y$grpvec # vector id for the 1st tier reporting groups (aka groupvec)
+  p2_grps <- dat_in$y2$grpvec # vector id for the 2nd tier reporting groups
   sub_grp <- dat_in$sub_group
   grp_names_t1 <- dat_in$group_names_t1
   grp_names_t2 <- dat_in$group_names_t2
@@ -270,12 +270,17 @@ msgsi_mdl <- function(dat_in, nreps, nburn, thin, nchains, nadapt = 0, keep_burn
         if ((rep - nadapt) > n_burn & (rep - nadapt - n_burn) %% thin == 0) {
 
           it <- (rep - nadapt - n_burn) / thin
-          p_grp <- tapply(p, grps, sum)
-          p2_grp <- tapply(p2, p2_grps, sum)
+          # trace output in reporting groups
+          # p_grp <- tapply(p, grps, sum)
+          # p2_grp <- tapply(p2, p2_grps, sum)
+          # p_out[[it]] <- c(p_grp, it, ch)
+          # p2_out[[it]] <- c(p2_grp, it, ch)
+          # pp2_out[[it]] <- c(p_grp[-sub_grp], p2_grp * sum(p_grp[sub_grp]), it, ch)
 
-          p_out[[it]] <- c(p_grp, it, ch)
-          p2_out[[it]] <- c(p2_grp, it, ch)
-          pp2_out[[it]] <- c(p_grp[-sub_grp], p2_grp * sum(p_grp[sub_grp]), it, ch)
+          # trace output in collections
+          p_out[[it]] <- c(p, it, ch)
+          p2_out[[it]] <- c(p2, it, ch)
+          pp2_out[[it]] <- c(p[which(!grps %in% sub_grp)], p2 * sum(p[which(grps %in% sub_grp)]), it, ch)
[…]

### 2025-04-19 R/trace_plot.R

@@ -6,8 +6,9 @@
 #'   Default is 0 if you didn't save the burn-ins (keep_burn = FALSE).
 #' @param thin Number of thinning you set up when you ran the model.
 #'   Default is 1 (no thinning).
-#' @param name_order Arrange the reporting groups as you wish. Leave it empty
-#'   if you want to accept the default.
+#' @param pop_info Population information. A tibble with columns
+#'   collection (collection names), repunit (reporting unit names),
+#'   grpvec (group numbers), and optional origin (wild/hatchery).
 #'
 #' @return Trace plot in ggplot
 
@@ -26,26 +27,33 @@
 #' # trace plot
 #' tr_plot(obj = msgsi_out$trace_comb)
 
-tr_plot <- function (obj, nburn = 0, thin = 1, name_order = NULL) {
+tr_plot <- function (obj, nburn = 0, thin = 1, pop_info = NULL) {
 
-  if (is.null(name_order)) {
+  if (is.null(pop_info)) {
     name_order <- dplyr::select(obj, -c(itr, chain)) %>% colnames()
+    trace <- tidyr::pivot_longer({{ obj }}, cols = -c(chain, itr),
+                                 names_to = "repunit", values_to = "p")
+  } else {
+    name_order <- unique(pop_info$repunit)
+    trace <- tidyr::pivot_longer({{ obj }}, cols = -c(chain, itr), names_to = "collection") %>%
+      dplyr::left_join(pop_info, by = "collection") %>%
+      dplyr::summarise(p = sum(value), .by = c(chain, itr, repunit))
   }
 
-  tidyr::pivot_longer({{ obj }}, cols = -c(chain, itr)) %>%
-    dplyr::mutate(name = factor(name, levels = name_order)) %>%
+  trace %>%
+    dplyr::mutate(repunit = factor(repunit, levels = name_order)) %>%
     ggplot2::ggplot() +
-    ggplot2::geom_line(ggplot2::aes(x = itr, y = value, color = factor(chain))) +
+    ggplot2::geom_line(ggplot2::aes(x = itr, y = p, color = factor(chain))) +
     {if (nburn > 0) {
       ggplot2::annotate("rect", fill = "red", alpha = 0.15,
                         xmin = 0, xmax = nburn/thin, ymin = -Inf, ymax = Inf)
     }} +
-    ggplot2::facet_grid(name ~ ., scales = "free") +
[…]

### 2025-04-19 R/msgsi_data.R
groups as tibbles

@@ -170,8 +170,13 @@ prep_msgsi_data <-
       iden = iden,
       nalleles = n_alleles_t1,
       nalleles2 = n_alleles_t2,
-      groups = base1$grpvec,
-      p2_groups = base2$grpvec,
+      groups = dplyr::select(base1, collection, repunit, grpvec), # base1$grpvec,
+      p2_groups = dplyr::select(base2, collection, repunit, grpvec), # base2$grpvec,
+      comb_groups = dplyr::select(base1, collection, repunit, grpvec) %>%
+        dplyr::filter(!grpvec %in% sub_group) %>%
+        dplyr::bind_rows({
+          dplyr::select(base2, collection, repunit, grpvec)
+        }),
       sub_group = sub_group,
       group_names_t1 = grp1_nms,
       group_names_t2 = grp2_nms,

### 2025-04-19 R/stra_est.R
option for new grouping

@@ -1,11 +1,13 @@
 
 #' Stratified estimator for Ms.GSI
 #'
-#' @param mdl_out Optional. Model output object name for combining group proportions and harvest of a single mixture.
+#' @param mdl_out Optional. Ms.GSI output object name for combining group proportions and harvest of a single mixture.
 #' @param path Where to find output from each mixture as a folder.
 #' @param mixvec Character vector of mixture sillies that are used to locate the folders where output .csv files lives, if `mdl_out` is not provided.
 #' @param catchvec Numeric vector of harvest for each mixture/stratum, must be in the same order as `mixvec`.
 #' @param cv Numeric vector of harvest estimate coefficients of variation for each stratum, must be the same order as `mixvec`.
+#' @param new_pop_info Population information for the new grouping. A tibble with columns
+#'   `repunit` and `new_repunit`. `repunit` is the names of the original reporting groups.
 #'
 #' @return A tibble of proportions and harvest numbers by reporting group for combined mixtures/strata.
 #' @importFrom magrittr %>%
@@ -13,10 +15,14 @@
 #'
 #' @examples
 #' \dontrun{
-#' stratified_estimator_msgsi(path = "test", mixvec = c("m1", "m2", "m3"), catchvec = c(4500, 5000, 3000), cv = c(0.5, 0.1 ,0.3))
+#' new_groups <- mdl_out$summ_comb %>% dplyr::select(group) %>%
+#'  dplyr::mutate(new_repunit = c(rep("broad", 9), rep("regional", 3))) %>%
+#'  dplyr::rename(repunit = group)
+#'
+#' stratified_estimator_msgsi(path = "test", mixvec = c("m1", "m2", "m3"), catchvec = c(4500, 5000, 3000), cv = c(0.5, 0.1 ,0.3), new_pop_info = new_groups)
 #' }
 #'
-stratified_estimator_msgsi <- function(mdl_out = NULL, path = NULL, mixvec, catchvec, cv = NULL) {
+stratified_estimator_msgsi <- function(mdl_out = NULL, path = NULL, mixvec, catchvec, cv = NULL, new_pop_info = NULL) {
 
   if (is.null(mdl_out) & is.null(path)) {
     stop("`Either provide a Ms.GSI output or a valid `path` to folders containing output .csv files for each mixture.")
@@ -35,6 +41,18 @@ stratified_estimator_msgsi <- function(mdl_out = NULL, path = NULL, mixvec, catc
 
   if (is.null(cv)) cv <- rep(0, length(catchvec))
 
[…]

### 2025-04-21 R/trace_plot.R
update document

@@ -8,7 +8,7 @@
 #'   Default is 1 (no thinning).
 #' @param pop_info Population information. A tibble with columns
 #'   collection (collection names), repunit (reporting unit names),
-#'   grpvec (group numbers), and optional origin (wild/hatchery).
+#'    and grpvec (group numbers).
 #'
 #' @return Trace plot in ggplot
 
@@ -25,7 +25,7 @@
 #' msgsi_out <- msgsi_mdl(msgsi_dat, nreps = 25, nburn = 15, thin = 1, nchains = 1)
 #'
 #' # trace plot
-#' tr_plot(obj = msgsi_out$trace_comb)
+#' tr_plot(obj = msgsi_out$trace_comb, pop_info = msgsi_out$comb_groups)
 
 tr_plot <- function (obj, nburn = 0, thin = 1, pop_info = NULL) {
 
